---
output: pdf_document
---
# The Effect of Vitamin C on Tooth Growth in Guinea Pigs

The response is the length of odontoblasts (teeth) in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1, and 2 mg) with each of two delivery methods (orange juice or ascorbic acid).

A data frame with 60 observations on 3 variables.

[,1]   len	 numeric	 Tooth length
[,2]	 supp	 factor	 Supplement type (VC or OJ).
[,3]	 dose	 numeric	 Dose in milligrams.

#1. Load the ToothGrowth data and perform some basic exploratory data analyses 
```{r}
library(ggplot2)
data(ToothGrowth)
ggplot(ToothGrowth, aes(dose, len))+
geom_jitter(aes(colour = factor(supp)))
```

#2. Provide a basic summary of the data.
```{r}
head(ToothGrowth)
summary(ToothGrowth)
summary(ToothGrowth$len)
summary(ToothGrowth$dose)
summary(ToothGrowth$supp)
```

#3. Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose. (Use the techniques from class even if there's other approaches worth considering)
```{r}
chisq.test(ToothGrowth$len,ToothGrowth$dose)
```
The output includes an Chi-squared statistic (X-squared) , the relevant degrees of 
freedom and an associated p-value. Here we would accept the null hypothesis that 
there is no association between the tooth length and dose, 
as there is a p-value larger than 0.05.
```{r}
chisq.test(ToothGrowth$len,ToothGrowth$supp)
```
Here we would accept the null hypothesis that 
there is no association between the tooth length and supplement type, 
as there is a p-value much larger than 0.05.

#4. State your conclusions and the assumptions needed for your conclusions. 
P-value for association between the tooth length and supplement type is larger than 
between the tooth length and dose. My conclusion therefore is that dose affects 
tooth length more than supplement type. (For more accurate conclusion additional 
tests are required)


